### 2024-09-30 esop25/cpj.tex
checkpoint

@@

Given a valid typing, we need to conservatively approximate the
information accessible by the adversary, who will have control over
all corrupt clients in $C$ given a partitioning $H,C$. In particular,
if the adversary has access to an encypted value and another value
that is dependent on its one-time-pad key-- i.e., access to values
with types of the forms:
$$
\setit{\cty{\rx{x}{\cid}}{\ty}} \qquad \setit{\rx{x}{\cid}, \ldots} 
$$
then we can conservatively assume that the adversary can decrypt the
value of type $\ty$.

\begin{theorem}
  If $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is valid and there exists no $H,C$ 
  and  $\sx{w}{\cid}$ for $\cid \in H$ with $\leakj{\Gamma}{C}{\setit{\sx{w}{\cid}}}$,
  then $\prog$ satisfies gradual release.
\end{theorem}

>>>>

Given a valid typing, we can leverage structural type information to
conservatively approximate the information accessible by the
adversary who has control over all corrupt clients in $C$ given
a partitioning $H,C$. In particular, if the adversary has access to an
encypted value and another value that is dependent on its one-time-pad
key-- i.e., access to values with types of the forms:
$$
\setit{\cty{\rx{x}{\cid}}{\ty}} \qquad \setit{\rx{x}{\cid}, \ldots} 
$$
then we can conservatively assume that the adversary can decrypt the
value of type $\ty$ and thus have access to those values.

In Figure \ref{fig-leakj} we define derivation rules for the
``leakage'' judgement $\leakj{\Gamma}{C}{\ty}$ which intuitively says
that given a protocol with type environment $\Gamma$ and corrupt
clients $C$, the adversary may be able to observe dependencies on
values of type $\ty$ in their adversarial messages.  The real aim of
this relation is to determine if
$\leakj{\Gamma}{C}{\setit{\sx{w}{\cid}}}$ with $\cid \in H$-- that is,
if the adversary may observe dependencies on honest secrets.

Our main type safety result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\cnote{Need to define gradual release... should probably have a section
  where we summarize hyperproperties.}
\begin{theorem}
  If $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is valid and there exists no $H,C$ 
  and  $\sx{w}{\cid}$ for $\cid \in H$ with $\leakj{\Gamma}{C}{\setit{\sx{w}{\cid}}}$,
  then $\prog$ satisfies gradual release.
\end{theorem}

@@

Of course, it is important to recall from \cite{skalka-near-ppdp24}
that gradual release does \emph{not} imply passive security, since it
only concerns adversarial messages, but not public reveals of outputs
where dependencies on input secrects can occur even in secure
protocols.
